Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-13 doc/sc2012/related.tex
Fixing minor grammar

Galois is programming system based on optimistic parallelism that dynamically detects 
memory conflicts between concurrent threads at the very
fine granularity of object accesses.  To achieve reasonable performance
Galois supports a partitioning interface for breaking up data structures \cite{Kulkarni08}.  
Galois relies on shared memory
and only leverages partitioning for coarser locking and conflict detection.
Several other recent efforts have proposed task schedulers
based on dynamic detection of memory conflicts, but these also have assumed
underlying shared memory hardware \cite{VTN11,Tzenakis12,EYJD12}.

>>>>

Galois is a programming system based on optimistic parallelism that dynamically detects 
memory conflicts between concurrent threads at the very
fine granularity of object accesses.  To achieve reasonable performance
Galois supports a partitioning interface for breaking up data structures \cite{Kulkarni08}.  
Galois relies on shared memory
and only leverages partitioning for coarser locking and conflict detection.
Several other recent efforts have proposed task schedulers
based on dynamic detection of memory conflicts, but these also have assumed
underlying shared memory hardware \cite{VTN11,Tzenakis12,EYJD12}.
